Bacon: A GPU Programming Language With Just in Time Specialization

### 2011-08-18 doc/Paper/Paper.tex
Some improvements to the paper.

\section{Previous and Similar Work}

@@

The two optimizations that are performed by the Bacon library are
constant propagation and loop unrolling. Constant propagation
calculates the values of all the variables that have been marked as
\tt{const} by the programmer. If the value of any of these variables
cannot be computed from the specialized arguments to the kernel, the
Bacon runtime will throw an exception.  This information is used to
construct a symbol table, and references to these variables are
replaced with their constant integer values in the generated OpenCL
code. Loop unrolling is then performed on any loops that can be
statically analyzed.

Loop unrolling is included because neither the AMD nor Nvidia OpenCL
compilers do it by default, and manually unrolling loops is time
consuming and error prone. Loop unrolling in Bacon is an even more
powerful optimization than usual due to the ability to either fully
unroll loops or to unroll them by a factor that is guaranteed to
evenly divide the iteration count because array sizes are always known
due to just in time specialization.

>>>>

\section{Previous Work}

@@

The two optimizations that are performed by the Bacon library are
constant propagation and loop unrolling. Constant propagation
calculates the values of all the variables that have been marked as
{\tt const} by the programmer. If the value of any of these variables
cannot be computed from the specialized arguments to the kernel, the
Bacon runtime will throw an exception.  This information is used to
construct a symbol table, and references to these variables are
replaced with their constant integer values in the generated OpenCL
code. Loop unrolling is then performed on any loops that can be
statically analyzed.

Loop unrolling is included because neither the AMD nor Nvidia OpenCL
compilers do it by default and manually unrolling loops is time
consuming and error prone. Loop unrolling in Bacon is an even more
powerful optimization than usual due to the ability to either fully
unroll loops or to unroll them by a factor that is guaranteed to
evenly divide the iteration count because array sizes are always known
due to just in time specialization.
